Supplementary Report for the article *Functional diversity can facilitate the collapse of an undesirable ecosystem state*

### 2023-01-31 reports/supplement/supplement_0.9.1.Rmd
update supplement

For comparability with the [Bush et al publication 2017](https://www.nature.com/articles/s41467-017-00912-x), we use a log-scale of the oxygen diffusivity gradient when displaying the effect of trait variation on tipping point positions. Throughout the text, we do not make comparisons when their outcome would depend on the decision to measure effect sizes on a log-scale of the environmental driver. For example, we compare the direction but not the magnitude of the diversity effects of the three functional groups on the resilience of the ecosystem state that they dominate (CB: oxic state, i.e. oxic-anoxic tipping point; SB and PB: anoxic state, i.e. anoxic-oxic tipping point). On a logarithmic scale, the magnitude of these diversity effects depends on whether a tipping point is located at low or high oxygen diffusivity (Figure 13.1) and therefore on whether a group dominates the oxic or the anoxic state.

>>>>

For comparability with the [Bush et al publication 2017](https://www.nature.com/articles/s41467-017-00912-x), we use a log-scale of the oxygen diffusivity gradient when displaying the effect of trait variation on tipping point positions. Throughout the text, we do not make comparisons when their outcome would depend on our decision to quantify diversity effects on a log-scale of oxygen diffusivity. For example, we compare the direction but not the magnitude of the diversity effects of the three functional groups on the resilience of the ecosystem state that they dominate (CB: oxic state, i.e. oxic-anoxic tipping point; SB and PB: anoxic state, i.e. anoxic-oxic tipping point). On a logarithmic scale, the magnitude of these diversity effects depends on whether a tipping point is located at low or high oxygen diffusivity (Figure 13.1) and therefore on whether a group dominates the oxic or the anoxic state.
